Trends of downward SDR in Thessaloniki

### 2023-05-11 Article.Rmd
Commit 2023-05-11 12:17

<!--\tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!--\normalsize-->

>>>>

<!--\tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
cat('\n\n\\footnotesize\n\n')
pander::pander(pp,
               caption = "Table of trends and stats")
cat('\n\n\\normalsize\n\n')
```
<!--\normalsize-->
